D3064R0: How to Avoid OOTA Without Really Trying

### 2024-03-05 ootavacuous.tex
Fallout from reversing Listings 1 and 2
Now that Listings 1 and 2 have been swapped, the references to them
should be swapped as well.

Signed-off-by: Paul E. McKenney <paulmck@kernel.org>

The earlier examples shown in
Listings~\ref{lst:Simple Reordering}
and~\ref{lst:Simple OOTA}
can be recast as similar \co{herd7} litmus tests, as shown in
Listing~\ref{lst:Simple Reordering as Litmus Test}
on page~\pageref{lst:Simple Reordering as Litmus Test}
and Listing~\ref{lst:Causality Test Case 4}
on page~\pageref{lst:Causality Test Case 4}, respectively.
Other OOTA-related litmus tests may be found in
Appendix~\ref{app:Illustrative Litmus Tests}
and
Appendix~\ref{app:Litmus Tests from “Causality Test Cases"}.

>>>>

The earlier examples shown in
Listings~\ref{lst:Simple OOTA}
and~\ref{lst:Simple Reordering}
can be recast as similar \co{herd7} litmus tests, as shown in
Listing~\ref{lst:Causality Test Case 4}
on page~\pageref{lst:Causality Test Case 4}
and Listing~\ref{lst:Simple Reordering as Litmus Test}
on page~\pageref{lst:Simple Reordering as Litmus Test}, respectively.
Other OOTA-related litmus tests may be found in
Appendix~\ref{app:Illustrative Litmus Tests}
and
Appendix~\ref{app:Litmus Tests from “Causality Test Cases"}.
